\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-09 paper2015asml.tex
added some authors

\title{\LARGE \bf
Preparation of Papers for IEEE Sponsored Conferences \& Symposia*
}

\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small albert.author@papercept.net}}%
\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small b.d.researcher@ieee.org}}%
}

>>>>

\title{\LARGE \bf
WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators
}

\author{Arjun Menon$^{1}$, Sachin Chitta$^{1}$, Mark Moll$^{2}$, Lydia Kavraki$^{2}$% <-this % stops a space
\thanks{*This work was supported by ...}% <-this % stops a space
\thanks{$^{1}$SRI International, Menlo Park, CA
        {\tt\small arjun.menon@sri.com, sachin.chitta@sri.com}}%
\thanks{$^{2}$Rice University, Department of Computer Science, Houston, TX
        {\tt\small mmoll@rice.edu, kavraki@rice.edu}}%
}
